% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Casey M. Beach}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{
New Relic \\
Southwest 5th Avenue \#2700 \\
Portland Oregon \\
}

\begin{center}
{\large\bf Casey M. Beach}
\end{center}
\medskip\hrule height 1pt
\begin{center}
6604 83rd Avenue,\\
Portland, OR 97266 \\
(541) 990-8978 
\end{center} 
\vspace{1in}

 
\opening{To whom it may concern,} 
\begin{flushleft} 

\noindent I'm writing to inquire about the open position titled Senior Software Engineer - Go High Performance. I have 
been working for Cambia for nearly two years and have decided to start exploring the market.

\noindent For the past two years I've been working for the PaaS team at Cambia. While at Cambia I have pushed hard
to bring cutting edge technology into the fold. I architected and developed several iterations of our team's build and 
deploy pipeline which currently deploys dozens of docker based nodejs services. I have also worked on numerous nodejs services
for Cambia. Finally, I have a long history with Python and Scala development.

\noindent Thank you for taking the time to read through this letter. I would like to encourage you
contact me at any time via phone (541-990-8978) or email (beachc@gmail.com). I am looking forward to 
discovering my place at New Relic.

\end{flushleft}
\closing{Sincerely,} 
\vfill % forces letterhead to top of page
\end{letter}
\end{document}
